### 2014-11-11 tex/heap.tex
Minor checkpoint

\section{Heap: A Bi-partiate Graph}

The heap in this work is a labeled bipartite graph consisting of
references, $\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine
syntax in \figref{fig:machine-syntax} defines that graph in
$\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference map. As
done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as
partial functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is
the set of location-constraint pairs in the heap associated with the
given reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is
the reference associated with the given location-field pair in the
heap.

As the updates to $\cfgnt{L}$ and $\cfgnt{R}$ are complex in the
machine semantics, predicate calculus is used to describe updates to
the functions. Consider the following example where $\cfgnt{l}$ is
some location and$\rho$ is a set of references.
\[
\cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}][\forall \cfgnt{r}^\prime \in \rho\ \lp \cfgnt{r}^\prime \mapsto \lp \cfgt{true}\ l_\mathit{null}\rp \rp ]
\]
The new partial function $\cfgnt{L}^\prime$ is just like $\cfgnt{L}$
only it remaps $\cfgnt{r}$, and it remaps all the references in
$\rho$.

@@

You can think references as a pointers to sets of locations. More
concretely, a reference is an integer that the $R$ function maps to a
set of constraint, location pairs that define where it points
to. Within a machine state, references are string encodings of
integers.

\begin{definition}
The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
 $$\mathcal{R} = \mathbb{N}$$
\end{definition}

In order to make the distinction between different types of references, we partition the set of references using modular arithmetic. Stack references are those references which are created as a result of a field read. The total number of references in a representing state and a represented state are generally not the same. However, the number of references on the stack in either state is always the same.

\begin{definition}
The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
 $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
\end{definition}

Input heap references are references that exist prior to program execution in the symbolic input heap. While this set of references may be infinite, they are discovered one at a time via lazy initialization.

\begin{definition}
The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
 $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
\end{definition}

\begin{definition}
The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
 $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
\end{definition}

\begin{definition}
For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
\begin{align}
 f^\rightarrow &= \{ f(a) \mid a \in A\}\\
 f^\leftarrow &= \{ a \mid f(a) \in B \}
 \end{align}
 The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
 \begin{align}
 f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
 f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
 \end{align}
 Where $C \subset A$ and $D \subset B$
\end{definition}

A special reference, $\cfgnt{r}_\mathit{un}$, and location,
$\cfgnt{l}_\mathit{un}$, is introduced to support lazy
initialization. The '$\mathit{un}$' is to indicate the reference or
location is uninitialized at the point of execution.

>>>>

\subsection{Heaps as Bipartite Graphs}
An important aspect, and a novel contribution, of symbolic heaps its
representation as a labeled bipartite graph consisting of
references, $\cfgnt{r}$, and constraint location pairs,
$\lp\phi\ \cfgnt{l}\rp$. The heap structure conveys that the actual
location pointed to by a reference is conditional on aliasing
relationships within the heap. In this way, the graph represents sets
of heaps with the conditions under which those heaps exist.

The machine syntax in \figref{fig:machine-syntax} defines that graph
in $\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference
map. As done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are
treated as partial functions where $\cfgnt{L}(r) =
\{(\phi\ \cfgnt{l})\ ...\}$ is the set of location-constraint pairs in
the heap associated with the given reference, and
$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
associated with the given location-field pair in the heap. Predicate
calculus is used to describe the more complex updates to the heap in
the semantics.

There are several properties of the heap that are invariant and
important to the correctness of the algorithm.
\begin{compactitem}
\item ADD REFERENCES ARE IMMUTABLE
\end{compactitem}

@@

DEFINE $\rsym$ and $\rgse$.

### 2014-11-11 tex/proofs.tex
Minor checkpoint

>>>>

\begin{definition}
The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
 $$\mathcal{R} = \mathbb{N}$$
\end{definition}

In order to make the distinction between different types of references, we partition the set of references using modular arithmetic. Stack references are those references which are created as a result of a field read. The total number of references in a representing state and a represented state are generally not the same. However, the number of references on the stack in either state is always the same.

\begin{definition}
The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
 $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
\end{definition}

Input heap references are references that exist prior to program execution in the symbolic input heap. While this set of references may be infinite, they are discovered one at a time via lazy initialization.

\begin{definition}
The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
 $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
\end{definition}

\begin{definition}
The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
 $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
\end{definition}

\begin{definition}
For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
\begin{align}
 f^\rightarrow &= \{ f(a) \mid a \in A\}\\
 f^\leftarrow &= \{ a \mid f(a) \in B \}
 \end{align}
 The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
 \begin{align}
 f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
 f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
 \end{align}
 Where $C \subset A$ and $D \subset B$
\end{definition}

A special reference, $\cfgnt{r}_\mathit{un}$, and location,
$\cfgnt{l}_\mathit{un}$, is introduced to support lazy
initialization. The '$\mathit{un}$' is to indicate the reference or
location is uninitialized at the point of execution.

\begin{definition}
\label{def:state}
The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
\end{definition}

\begin{definition}
\label{def:initstate}
$\mathcal{S}_0$ is defined as the set of \textbf{initial states}. An
initial state is a state meeting the following conditions: The range
of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the
function R is defined only for location $l_0$, and for any field $f$,
$R(l_0,f)$ returns $r_{un}$.
\end{definition}

The rewrite rules that define the Javalite semantics are presented in
the supplemental document accompanying the paper.

\begin{definition}
A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary
relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times
\mathcal{S} $, which relates machine states with successor states. Two
important state transition relations are \textbf{GSE} $\rgse$ and
\textbf{symbolic} $\rsym$. Each of these use a separate relation for
initialization: $\rinit$ for GSE and $\rsum$ for symbolic. All of
these transition relations are defined in \figref{fig:lazy},
\figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
\end{definition}
